---
title: "Introduction to R-1, Variables and Datatypes"
output: html_notebook
---

This is first notebook in the set. It is going to give you a basic understanding and working knowledge of the language.

## Simple Operations
To get comfortable with R we will carry out few basic calculations which we are very familair with. 
- Addition operator (+)
- Subtraction operator (-)
- Multiplication operator (*)
- Division Operator (/)  
- Integer Division (%/%)
- Modulus Operator (%%)

```{r}
# Simple arithmetic to get things started
10+2 # Addition
10-2 # Subtraction
10 * 2 # Multiplication
10/2 # division
10 %% 2 # Modulus
10 %/% 3 # Integer division

```

R allows us to store data, which we can used anywhere in our program and we are not just limited to basic calculations. R stores information inside something called an "Object". Each of these objects can be given a name and when we want to use that information we can recall it by using the name. 

```{r}
# Storing information about rockets
name <- "falcon heavy"
maxPayload <- 63800
elephantWeight <- 4800

# If we were curious how many elephants we can send to space in falcon heavy we can calculate that using the information we have stored.
numberOfElephants <- maxPayload %/% elephantWeight # we want integer division as we want to take whole living elephants
numberOfElephants
```
# Storing Data
The name of the object or "*variable*" is places on the left hand side and operator (<-) assigns value of the "*expression*" on the right to it. In the example above, "falcon heavy" is stored in our program under the variable "name"

## Naming variables 
You should name or variables in a way that they are explicit and can be understood easily. You want to have variable names like (x) or (y). In a program with hundred of libe of code you will have to scroll up to your assignment line to figure out what is x referring to. 

There are also limitation ti what you can name your variables. Your name cannot start with a number and it cannot have special symbols that we use as *operators or other such as @, ! or ^*.

```{r}
ls()
# ls function gives you list of all the variable names that are currently in use 
```


# Order of Execution
In R, program is execution sequentially, element by element